Reproducibility in plant pathology: where do we stand and a way forward

### 2022-05-01 analysis/paper/paper.Rmd
remove duplicate call to load extrafont lib
Remove text on overall scores to earlier section

library("extrafont")
font_import()
```

@@

Out of the `r nrow(rrpp)` articles that were evaluated, `r length(which(rrpp$reproducibility_score == 0))` articles scored 0% out of a possible 100% for reproducibility.
The mean value was `r round(mean(rrpp$reproducibility_score), 1)`% and the median value was `r round(median(rrpp$reproducibility_score), 1)`%.
There were `r length(which(rrpp$reproducibility_score == 100))` (`r round(length(which(rrpp$reproducibility_score == 100))/nrow(rrpp), 2) * 100`%) articles that scored 100% or were classed as fully reproducible.

>>>>

font_import()
```

@@
